---
title: "Model Diagnostics"
author: "Nick Allen"
date: "November 12, 2014"
output: html_document
---

```{r, echo=FALSE, message=FALSE, results='hide', include=FALSE}
setwd ("..")
library (ProjectTemplate)
library (knitr)
load.project ()

opts_chunk$set(warning=FALSE, message=FALSE)
```

Place a hard limit on the number of test phrases to predict.

```{r}
count <- min (30000, nrow (test.ngrams))
comma (count)
```

Choose phrases to predict at random.

```{r, results='hide'}
p <- count / nrow (test.ngrams)
test.ngrams [, test := as.logical (rbinom (n = nrow (test.ngrams), size = 1, prob = p))]
```

Calculate the probability of each phrase.

```{r, results='hide'}
test.ngrams [test == TRUE, p := phrase_probability (phrase, ngrams), by = phrase]
```

Use the model to predict the next word.

```{r, results='hide'}
test.ngrams [test == TRUE, word_hat := predict_next_word (context, ngrams), by = phrase]
test.ngrams [test == TRUE, correct := word == word_hat ]
```

How many of the test phrases were predicted accurately?

```{r}
correct <- sum (test.ngrams$correct, na.rm = TRUE)
percent (correct / count)
```

How many did the null model predict accurately?

```{r}
correct <- nrow (test.ngrams [test == TRUE & word == "the"])
percent (correct / count)
```

```{r, results='hide', echo=FALSE}
# what words are being predicted correctly
words <- test.ngrams [test == T, list ('correct'  = sum (correct),
                                       'total'    = .N,
                                       'accuracy' = (sum (correct) / .N) * 100
                                       ), by = word]

# only keep those with significant number of occurrences
words <- words [total > 3]
```

What types of words were predicted accurately?

```{r}
head (words [order (accuracy, decreasing = T)][accuracy > 10], n = 50)
```

What types of were NOT predicted accurately?

```{r}
head (words [order (accuracy, decreasing = F)], n = 50)
```

