---
title: "Quiz 2"
author: "Nick Allen"
date: "November 6, 2014"
output: html_document
---

```{r, echo=FALSE, message=FALSE, results='hide', include=FALSE}
setwd ("..")
library (ProjectTemplate)
library (knitr)
load.project ()

opts_chunk$set(warning=FALSE, message=FALSE)
```

### Question 1

The guy in front of me just bought a pound of bacon, a bouquet, and a case of

* pretzels
* cheese
* (A) beer
* soda

```{r, warning=FALSE}
q <- "The guy in front of me just bought a pound of bacon, a bouquet, and a case of"

p <- list (pretzels = phrase_probability (paste (q, "pretzels"), ngrams),
           cheese   = phrase_probability (paste (q, "cheese"), ngrams),
           beer     = phrase_probability (paste (q, "beer"), ngrams),
           soda     = phrase_probability (paste (q, "soda"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 2

You're the reason why I smile everyday. Can you follow me please? It would mean the

* universe
* best
* (A) world
* most

```{r, warning=FALSE}
q <- "You're the reason why I smile everyday. Can you follow me please? It would mean the"

p <- list (universe = phrase_probability (paste (q, "universe"), ngrams),
           best     = phrase_probability (paste (q, "best"), ngrams),
           world    = phrase_probability (paste (q, "world"), ngrams),
           most     = phrase_probability (paste (q, "most"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 3

Hey sunshine, can you follow me and make me the

* (A) happiest
* saddest
* smelliest
* bluest

```{r, warning=FALSE}
q <- "Hey sunshine, can you follow me and make me the"

p <- list (happiest = phrase_probability (paste (q, "happiest"), ngrams),
           saddest = phrase_probability (paste (q, "saddest"), ngrams),
           smelliest = phrase_probability (paste (q, "smelliest"), ngrams),
           bluest = phrase_probability (paste (q, "bluest"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 4

Very early observations on the Bills game: Offense still struggling but the

* X players
* referees
* defense
* (?) crowd

```{r, warning=FALSE}
q <- "Very early observations on the Bills game: Offense still struggling but the"

p <- list (players = phrase_probability (paste (q, "players"), ngrams),
           referees = phrase_probability (paste (q, "referees"), ngrams),
           defense = phrase_probability (paste (q, "defense"), ngrams),
           crowd = phrase_probability (paste (q, "crowd"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 5

Go on a romantic date at the

* grocery
* mall
* movies
* (A) beach

```{r, warning=FALSE}
q <- "Go on a romantic date at the"

p <- list (grocery = phrase_probability (paste (q, "grocery"), ngrams),
           mall = phrase_probability (paste (q, "mall"), ngrams),
           movies = phrase_probability (paste (q, "movies"), ngrams),
           beach = phrase_probability (paste (q, "beach"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 6

Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my

* (A) way
* horse
* motorcycle
* phone

```{r, warning=FALSE}
q <- "Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my"

p <- list (way = phrase_probability (paste (q, "way"), ngrams),
           horse = phrase_probability (paste (q, "horse"), ngrams),
           motorcyle = phrase_probability (paste (q, "motorcycle"), ngrams),
           phone = phrase_probability (paste (q, "phone"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 7

Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some

* years
* thing
* weeks
* (A) time

```{r, warning=FALSE}
q <- "Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some"

p <- list(years = phrase_probability (paste (q, "years"), ngrams),
          thing = phrase_probability (paste (q, "thing"), ngrams),
          weeks = phrase_probability (paste (q, "weeks"), ngrams),
          time = phrase_probability (paste (q, "time"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 8

After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little

* X eyes
* (?) fingers
* toes
* ears

```{r, warning=FALSE}
q <- "After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little"

p <- list (eyes = phrase_probability (paste (q, "eyes"), ngrams),
           fingers = phrase_probability (paste (q, "fingers"), ngrams),
           toes = phrase_probability (paste (q, "toes"), ngrams),
           ears = phrase_probability (paste (q, "ears"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 9

Be grateful for the good times and keep the faith during the

* hard
* sad
* (A) bad
* worse

```{r, warning=FALSE}
q <- "Be grateful for the good times and keep the faith during the"

p <- list (hard = phrase_probability (paste (q, "hard"), ngrams),
           sad = phrase_probability (paste (q, "sad"), ngrams),
           bad = phrase_probability (paste (q, "bad"), ngrams),
           worse = phrase_probability (paste (q, "worse"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 10

If this isn't the cutest thing you've ever seen, then you must be

* insensitive
* asleep
* callous
* (A) insane

```{r, warning=FALSE}
q <- "If this isn't the cutest thing you've ever seen, then you must be"

p <- list (insensitive = phrase_probability (paste (q, "insensitive"), ngrams),
           asleep = phrase_probability (paste (q, "asleep"), ngrams),
           callous = phrase_probability (paste (q, "callous"), ngrams),
           insance = phrase_probability (paste (q, "insane"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


