---
title: "Quiz 2"
author: "Nick Allen"
date: "November 6, 2014"
output: html_document
---

```{r, echo=FALSE, message=FALSE, results='hide'}
setwd ("..")
library (ProjectTemplate)
load.project ()
```


### Question 1

The guy in front of me just bought a pound of bacon, a bouquet, and a case of

* pretzels
* cheese
* beer
* soda

```{r, warning=FALSE}
q <- "The guy in front of me just bought a pound of bacon, a bouquet, and a case of"
phrase_probability (paste (q, "pretzels"), ngrams)
phrase_probability (paste (q, "cheese"), ngrams)
phrase_probability (paste (q, "beer"), ngrams)
phrase_probability (paste (q, "soda"), ngrams)
```


### Question 2

You're the reason why I smile everyday. Can you follow me please? It would mean the

* universe
* best
* world
* most

```{r, warning=FALSE}
q <- "You're the reason why I smile everyday. Can you follow me please? It would mean the"
phrase_probability (paste (q, "universe"), ngrams)
phrase_probability (paste (q, "best"), ngrams)
phrase_probability (paste (q, "world"), ngrams)
phrase_probability (paste (q, "most"), ngrams)
```

### Question 3

Hey sunshine, can you follow me and make me the

* happiest
* saddest
* smelliest
* bluest

```{r, warning=FALSE}
q <- "Hey sunshine, can you follow me and make me the"
phrase_probability (paste (q, "happiest"), ngrams)
phrase_probability (paste (q, "saddest"), ngrams)
phrase_probability (paste (q, "smelliest"), ngrams)
phrase_probability (paste (q, "bluest"), ngrams)
```

### Question 4

Very early observations on the Bills game: Offense still struggling but the

* players
* referees
* defense
* crowd

```{r, warning=FALSE}
q <- "Very early observations on the Bills game: Offense still struggling but the"
phrase_probability (paste (q, "players"), ngrams)
phrase_probability (paste (q, "referees"), ngrams)
phrase_probability (paste (q, "defense"), ngrams)
phrase_probability (paste (q, "crowd"), ngrams)
```

### Question 5

Go on a romantic date at the

* grocery
* mall
* movies
* beach

```{r, warning=FALSE}
q <- "Go on a romantic date at the"
phrase_probability (paste (q, "grocery"), ngrams)
phrase_probability (paste (q, "mall"), ngrams)
phrase_probability (paste (q, "movies"), ngrams)
phrase_probability (paste (q, "beach"), ngrams)
```

### Question 6

Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my

* way
* horse
* motorcycle
* phone

```{r, warning=FALSE}
q <- "Well I'm pretty sure my granny has some old bagpipes in her garage I'll dust them off and be on my"
phrase_probability (paste (q, "way"), ngrams)
phrase_probability (paste (q, "horse"), ngrams)
phrase_probability (paste (q, "motorcycle"), ngrams)
phrase_probability (paste (q, "phone"), ngrams)
```

### Question 7

Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some

* years
* thing
* weeks
* time

```{r, warning=FALSE}
q <- "Ohhhhh #PointBreak is on tomorrow. Love that film and haven't seen it in quite some"
phrase_probability (paste (q, "years"), ngrams)
phrase_probability (paste (q, "thing"), ngrams)
phrase_probability (paste (q, "weeks"), ngrams)
phrase_probability (paste (q, "time"), ngrams)
```

### Question 8

After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little

* eyes
* fingers
* toes
* ears

```{r, warning=FALSE}
q <- "After the ice bucket challenge Louis will push his long wet hair out of his eyes with his little"
phrase_probability (paste (q, "eyes"), ngrams)
phrase_probability (paste (q, "fingers"), ngrams)
phrase_probability (paste (q, "toes"), ngrams)
phrase_probability (paste (q, "ears"), ngrams)
```

### Question 9

Be grateful for the good times and keep the faith during the

* hard
* sad
* bad
* worse

```{r, warning=FALSE}
q <- "Be grateful for the good times and keep the faith during the"
phrase_probability (paste (q, "hard"), ngrams)
phrase_probability (paste (q, "sad"), ngrams)
phrase_probability (paste (q, "bad"), ngrams)
phrase_probability (paste (q, "worse"), ngrams)
```

### Question 10

If this isn't the cutest thing you've ever seen, then you must be

* insensitive
* asleep
* callous
* insane

```{r, warning=FALSE}
q <- "If this isn't the cutest thing you've ever seen, then you must be"
phrase_probability (paste (q, "insensitive"), ngrams)
phrase_probability (paste (q, "asleep"), ngrams)
phrase_probability (paste (q, "callous"), ngrams)
phrase_probability (paste (q, "insane"), ngrams)
```


