---
title: "Quiz 3"
author: "Nick Allen"
date: "November 11, 2014"
output: html_document
---

```{r, echo=FALSE, message=FALSE, results='hide', include=FALSE}
setwd ("..")
library (ProjectTemplate)
library (knitr)
load.project ()

opts_chunk$set(warning=FALSE, message=FALSE)
```

### Question 1

```{r}
q <- "When you breathe, I want to be the air for you. I'll be there for you, I'd live and I'd"
```

* eat
* give
* sleep
* die

```{r}
p <- list (eat = phrase_probability (paste (q, "eat"), ngrams),
           give = phrase_probability (paste (q, "give"), ngrams),
           sleep = phrase_probability (paste (q, "sleep"), ngrams),
           die = phrase_probability (paste (q, "die"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 2

```{r}
q <- "Guy at my table's wife got up to go to the bathroom and I asked about dessert and he started telling me about his"
```

* spiritual
* marital
* financial
* horticultural

```{r}
p <- list (spiritual = phrase_probability (paste (q, "spiritual"), ngrams),
           marital = phrase_probability (paste (q, "marital"), ngrams),
           financial = phrase_probability (paste (q, "financial"), ngrams),
           horticultural = phrase_probability (paste (q, "horticultural"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 3

```{r}
q <- "I'd give anything to see arctic monkeys this"
```

* morning
* decade
* weekend
* month

```{r}
p <- list (morning = phrase_probability (paste (q, "morning"), ngrams),
           decade = phrase_probability (paste (q, "decade"), ngrams),
           weekend = phrase_probability (paste (q, "weekend"), ngrams),
           month = phrase_probability (paste (q, "month"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 4

```{r}
q <- "Talking to your mom has the same effect as a hug and helps reduce your"
```

* sleepiness
* happiness
* stress
* hunger

```{r}
p <- list (sleepiness = phrase_probability (paste (q, "sleepiness"), ngrams),
           happiness = phrase_probability (paste (q, "happiness"), ngrams),
           stress = phrase_probability (paste (q, "stress"), ngrams),
           hunger = phrase_probability (paste (q, "hunger"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 5

```{r}
q <- "When you were in Holland you were like 1 inch away from me but you hadn't time to take a"
```

* picture
* look
* minute
* walk

```{r}
p <- list (picture = phrase_probability (paste (q, "picture"), ngrams),
           look = phrase_probability (paste (q, "look"), ngrams),
           minute = phrase_probability (paste (q, "minute"), ngrams),
           walk = phrase_probability (paste (q, "walk"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 6

```{r}
q <- "I'd just like all of these ### Questions answered, a presentation of evidence, and a jury to settle the"
```

* account
* case
* incident
* matter

```{r}
p <- list (account = phrase_probability (paste (q, "account"), ngrams),
           case = phrase_probability (paste (q, "case"), ngrams),
           incident = phrase_probability (paste (q, "incident"), ngrams),
           matter = phrase_probability (paste (q, "matter"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 7

```{r}
q <- "I can't deal with unsymetrical things. I can't even hold an uneven number of bags of groceries in each"
```

* finger
* arm
* hand
* toe

```{r}
p <- list (finger = phrase_probability (paste (q, "finger"), ngrams),
           arm = phrase_probability (paste (q, "arm"), ngrams),
           hand = phrase_probability (paste (q, "hand"), ngrams),
           toe = phrase_probability (paste (q, "toe"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

### Question 8

```{r}
q <- "Every inch of you is perfect from the bottom to the"
```

* center
* top
* middle
* side

```{r}
p <- list (center = phrase_probability (paste (q, "center"), ngrams),
           top = phrase_probability (paste (q, "top"), ngrams),
           middle = phrase_probability (paste (q, "middle"), ngrams),
           side = phrase_probability (paste (q, "side"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 9

```{r}
q <- "I’m thankful my childhood was filled with imagination and bruises from playing"
```

* daily
* weekly
* inside
* outside

```{r}
p <- list (daily = phrase_probability (paste (q, "daily"), ngrams),
           weekly = phrase_probability (paste (q, "weekly"), ngrams),
           inside = phrase_probability (paste (q, "inside"), ngrams),
           outside = phrase_probability (paste (q, "outside"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```


### Question 10

```{r}
q <- "I like how the same people are in almost all of Adam Sandler's"
```

* pictures
* movies
* stories
* novels

```{r}
p <- list (pictures = phrase_probability (paste (q, "pictures"), ngrams),
           movies = phrase_probability (paste (q, "movies"), ngrams),
           stories = phrase_probability (paste (q, "stories"), ngrams),
           novels = phrase_probability (paste (q, "novels"), ngrams))

p [which.max (p)]
predict_next_word (q, ngrams)
```

